Multiset-trie data structure

### 2023-02-20 tex/tex/s_experiments.tex
Reviews.docx prepared. some responses to comments updated and added. associated tex files updated.

% anouncement of the experiments
In the following sections, we will present the behavior of the multiset-trie data 
structure in four experiments.
The first three experiments use artificially generated data, and the fourth experiment
uses real-world data. In the 
Experiment~\hyperref[s:exp1]{1} a special case of the multiset-trie is considered. 
Only sets are allowed to be stored in the data structure, i.e., the maximally allowed 
multiplicity is set to 1. The performance is measured with respect to the density 
of the multiset-trie.

@@

Finally, the fourth experiment on the multiset-trie uses real-world data. In 
Experiment~\hyperref[s:exp4]{4} the influence of the mapping $\phi$ is studied. 
The input data is obtained by mapping the real words from the English dictionary 
to the set of consecutive integers using the function $\phi.$ The experiment 
shows that the performance of the multiset-trie is noticeably influenced by 
different mappings $\phi.$ It also shows the usability of the multiset-trie in terms 
of real data demonstrating the high performance of search queries.

% 
%After all the experiments we present an empirical comparison of multiset-trie 
%data structure with B-tree based inverted index. We use inverted index 
%to store and retrieve multisets in the same way as it is described in the paper by 
%Helmer and Moerkotte~\cite{Helmer2003} for sets. In the comparison we use 
%three types of queries exact, submultiset and supermultiset retrieval.

@@

\begin{figure}
\center
\subcaptionbox{submsetExistence
\label{fig:e3m1}}{\includegraphics[width=.45\textwidth]{exp4-m1.pdf}}
\subcaptionbox{supermsetExistence
\label{fig:e3m2}}{\includegraphics[width=.45\textwidth]{exp4-m2.pdf}}
\caption{Exsitence functions in Experiment 3.}
\end{figure}

@@

>>>>

% anouncement of the experiments
In the following Sections 1-5 we will present the behavior of the multiset-trie data 
structure depending on the selected parameters as well as the comparative 
benchmark of the multiset-trie against B-tree implementation of inverted index. 
We start with experiments that are performed on an artificially generated data in 
order to give a general picture of the multiset-trie performance.

In the Experiment~\hyperref[s:exp1]{1} a special case of the multiset-trie is considered. 
Only sets are allowed to be stored in the data structure, i.e., the maximally allowed 
multiplicity is set to 1. The performance is measured with respect to the density 
of the multiset-trie.

@@

The fourth experiment on the multiset-trie uses real-world data. In 
Experiment~\hyperref[s:exp4]{4} the influence of the mapping $\phi$ is studied. 
The input data is obtained by mapping the real words from the English dictionary 
to the set of consecutive integers using the function $\phi.$ The experiment 
shows that the performance of the multiset-trie is noticeably influenced by 
different mappings $\phi.$ It also shows the usability of the multiset-trie in terms 
of real data demonstrating the high performance of search queries.

Finally, the empirical comparison of multiset-trie data structure with
B-tree based inverted index is presemted in Experiment~\hyperref[s:exp5]{5}. We use
inverted index to store and retrieve multisets in the same way as it
is described in the paper by Helmer and Moerkotte~\cite{Helmer2003}
for sets. In the comparison we use three types of queries: exact,
submultiset and supermultiset retrieval.

@@

\begin{figure}
\center
\subcaptionbox{submsetExistence
\label{fig:e3m1}}{\includegraphics[width=.45\textwidth]{exp4-m1.pdf}}
\subcaptionbox{supermsetExistence
\label{fig:e3m2}}{\includegraphics[width=.45\textwidth]{exp4-m2.pdf}}
\caption{Existence functions in Experiment 3.}
\end{figure}

@@

\subsection{Experiment 5} \label{s:exp5}

In this experiment, we demonstrate the performance of multiset-trie
data structure compared to the inverted index based on the
B-tree. Both data structures are implemented in the programming
language \CC, providing in this way an experimental setup for a fair
comparison \cite{akulich2019mstrie}.

%((Brief description of the implementation of the inverted files?))
The inverted index is implemented using an idea
from~\cite{Helmer2003}. An inverted index structure consists of two
parts: a dictionary and postings. In our case, a dictionary is
implemented as an in-memory B-tree where keys are all distinct values
from a domain represented by a set $\Sigma.$ The postings are
represented by lists of multisets that contain a particular element
from $\Sigma.$ Each list item in postings contains a cardinality of a
multiset, which speeds up the containment queries.

The experiment uses the input data for the construction of the given
data structure and the test data for the execution of the operations
on the given data structure. The input data comprises a set of
randomly generated multisets used for the construction of a data
structure. The test data includes the set of multisets together with
the operations that are evaluated. The input and test data were
generated with respect to parameters $\sigma$ and $n$ as presented in
xTable~\ref{t:benchmark}.

\begin{table}[h]
\center
\begin{tabular}{|c|c|}
\hline
$\sigma$ & $n$ \\
\hline
5		& 1\\
\hline
30	& 1 \\
\hline
5		& 3 \\
\hline
15	& 3 \\
\hline
30	& 3 \\
\hline
10	& 10 \\
\hline
\end{tabular}
\caption{Configuration of $\sigma$ and $n$ in benchmark.}
\label{t:benchmark}
\end{table}

We tested all three types of a query on all of the configurations from
Table 1 results in 18 experiments total, i.e., 6 experiments per
query type. In each experiment, we measured the average time consumed
by the data structure to process the query. The results of the exact
search, sub-multiset, and super-multiset search experiments are
presented in tables Table~\ref{t:res_ex}, Table~\ref{t:res_sub} and
Table~\ref{t:res_sup}, respectively.

\begin{table}[h]
\center
\begin{tabular}{|r|r|r|r|}
\hline
\multicolumn{1}{|c|}{$\sigma$} & 
\multicolumn{1}{c|}{$n$} & 
\multicolumn{1}{c|}{Multiset-trie ($\mu s$)} & 
\multicolumn{1}{c|}{Inverted index ($\mu s$)} \\
\hline
5		& 1 & 3.45 & 17782.35\\
\hline
30	& 1 & 4.18 & 24865.93\\
\hline
5		& 3 & 2.20 & 1508.81\\
\hline
15	& 3 & 4.39 & 2146.36\\
\hline
30	& 3 & 10.67 & 3639.97\\
\hline
10	& 10 & 6.93 & 384.05\\
\hline
\end{tabular}
\caption{Exact search.}
\label{t:res_ex}
\end{table}

\begin{table}[h]
\center
\begin{tabular}{|r|r|r|r|}
\hline
\multicolumn{1}{|c|}{$\sigma$} & 
\multicolumn{1}{c|}{$n$} & 
\multicolumn{1}{c|}{Multiset-trie ($\mu s$)} & 
\multicolumn{1}{c|}{Inverted index ($\mu s$)} \\
\hline
5		& 1			& 8.96 & 73500.84\\
\hline
30	& 1			& 17.33 & 547572.74\\
\hline
5		& 3			& 117.95 & 162360.43\\
\hline
15	& 3			& 20.74 & 443321.39\\
\hline
30	& 3 		& 23.75 & 947706.14\\
\hline
10	& 10		& 55.59 & 466022.68\\
\hline
\end{tabular}
\caption{Sub-multiset search.}
\label{t:res_sub}
\end{table}

\begin{table}[h]
\center
\begin{tabular}{|r|r|r|r|}
\hline
\multicolumn{1}{|c|}{$\sigma$} & 
\multicolumn{1}{c|}{$n$} & 
\multicolumn{1}{c|}{Multiset-trie ($\mu s$)} & 
\multicolumn{1}{c|}{Inverted index ($\mu s$)} \\
\hline
5		& 1 		& 10.63 & 63073.86\\
\hline
30	& 1 		& 14.65 & 449251.68\\
\hline
5		& 3 		& 171.04 & 163256.77\\
\hline
15	& 3 		& 43.42 & 425733.80\\
\hline
30	& 3 		& 22.06 & 729831.34\\
\hline
10	& 10 	& 58.32 & 373784.81\\
\hline
\end{tabular}
\caption{Super-multiset search.}
\label{t:res_sup}
\end{table}

We can see that multiset-trie outperforms the inverted index in all of the
experiments by up to 4 orders of magnitude. In an exact search,
multiset-trie has to traverse only up to $\sigma+1$ nodes to get a query
result. It can be seen from the results that with the increase of $\sigma$
the processing time for multiset-tire also increases. Multiplicity
also affects the processing time; however, this happens
passively. Multiplicity, or degree of a node $n$, defines the shape of
multisets that are stored in multiset-trie. Thus, it affects the
structure and density of the multiset-trie.

As for the inverted index, all three operations must first fetch all
postings for each particular element of a test multiset. Afterward,
the intersection of postings is computed to answer the query. The
operations use more processing time than a simple tree traversal,
which we can see from the results. Postings are filtered on-the-fly to
reduce the cost of the intersection.

Implementations of the sub-multiset and super-multiset are similar in
the case of the inverted file. The algorithm consists of the same
steps. First, the postings are fetched for each element of the test
multiset. Depending on the particular operation, postings are filtered
on-the-fly. Finally, the union or the intersection of the filtered set
of postings is computed. Note that the processing time increases with
the size of the inverted index because of the increased sizes of
postings.

In the case of multiset-trie, only a traversal of the tree is
required, which is much faster than the processing of postings, as we
can see from the results. In the worst case, the whole tree is
traversed, but the same is for an inverted file.

### 2023-02-20 tex/tex/s_operations.tex
Reviews.docx prepared. some responses to comments updated and added. associated tex files updated.

%
Let $\mathcal{M}$ be a multiset-trie and let $M$ be a set of multisets that are 
inserted into the multiset-trie $\mathcal{M}.$ We define a type \emph{Multiset} in 
order to use it as a representation of a multiset. The type \emph{Multiset} is 
an array $m$ of constant length $\sigma,$ where $i$-th cell represents the element 
$\phi^{-1}(i)$ from $\Sigma$ with multiplicity $m[i].$ From now on we 
agree that the first cell of an array has index 1. Let us have an example of a 
\emph{Multiset} instance with $\sigma = 2:$
%
\begin{center}
\begin{tabular}{ccc}
Multiset & & Instance of type Multiset \\
$\{ 1,1,2 \}$ & $\cong $ & 
\begin{tabular}{|c|c|}
\hline 
2 & 1 \\
\hline 
\multicolumn{1}{c}{\tiny 1} & \multicolumn{1}{c}{\tiny 2} \\
\end{tabular}
\end{tabular}
\end{center}
%
The operations supported by the multiset-trie data structure are as follows.
%
\begin{enumerate}
\item \textsc{insert}($\mathcal{M}$, $m$): inserts a multiset $m$ into 
$\mathcal{M}$ if $m\not\in M;$
%
\item \textsc{search}($\mathcal{M}$, $m$): returns true if a multiset $m\in M$ 
for a given $\mathcal{M},$ and returns false otherwise;
%
\item \textsc{delete}($\mathcal{M}$, $m$): returns true if a multiset $m$ was 
successfully deleted from $\mathcal{M},$ and returns false otherwise (in case 
$m\not\in M$);
%
\item \textsc{submsetExistence}($\mathcal{M}$, $m$, $dev$): returns true if 
there exists a $x\in M$ for a given $\mathcal{M}$ such that $x\subseteq m$ 
and $| x[i] - m[i] |\leq dev$ for $1\leq i\leq \sigma$, and returns false otherwise; 
%
\item \textsc{supermsetExistence}($\mathcal{M}$, $m$, $dev$): returns true if 
there exists a $x\in M$ for a given $\mathcal{M}$ such that $x\supseteq m$ 
and $| x[i] - m[i] |\leq dev$ for $1\leq i\leq \sigma$, and returns false otherwise; 
%
\item \textsc{getAllSubmsets}($\mathcal{M}$, $m$, $dev$): returns the set of multisets 
$\{ x \in M : x\subseteq m \wedge |x[i]-m[i]|\leq dev \}$ for a given 
$\mathcal{M},$ where $1\leq i\leq \sigma;$
%
\item \textsc{getAllSupermsets}($\mathcal{M}$, $m$, $dev$): returns the set of multisets 
$\{ x\in M : x\supseteq m \wedge |x[i]-m[i]|\leq dev \}$ for a given $\mathcal{M},$
where $1\leq i\leq \sigma.$
%
\end{enumerate}

In the following subsections we will present each operation of the multiset-trie 
data structure separately.

@@

\subsection{Insert} \label{s:insert}
The procedure \textsc{insert}($\mathcal{M}$, $m$) inserts a new instance $m$ of 
type Multiset into multiset-trie $\mathcal{M}$. If the complete path already 
exists, then procedure leaves the structure unchanged. Otherwise it extends 
partially existing or creates a new complete path. The procedure does not return 
any result. The pseudocode for procedure \textsc{insert} is presented in 
Algorithm~\ref{alg:insert}.

@@

\subsection{Delete} \label{s:delete}
The function \textsc{delete}($\mathcal{M},$ $m$) searches for the complete path 
that corresponds to $m$ in order to remove it. If the path can not be found, the 
function immediately returns false. During search, the function keeps track of the 
number of children for every node. It marks the nodes that have more than one child 
as \emph{parent nodes} and remembers the label of the child which is a potential node 
where the sub-tree will be cut to remove the multiset. The parent node is needed to 
perform a removal, because the multiset-tire is an explicit data structure. When search 
is completed, the function removes the sub-tree of the last found parent node, and 
returns true. In such a way after deletion all the prefixes for other multisets are 
preserved in $\mathcal{M}$ and $m$ is removed. The function \textsc{delete} is 
presented in Algorithm~\ref{alg:delete}.

@@

\subsection{Sub-multiset existence} \label{s:subexists}
The function \textsc{submsetExistence}($\mathcal{M},m,dev$) checks if there exists 
a multiset $x$ in $\mathcal{M},$ that satisfies the condition $x\subseteq m$ and 
$| x[i] - m[i] | \leq dev,$ where $1\leq i \leq \sigma.$ 
The function starts with searching for an exact match $x=m$ in $\mathcal{M},$ 
since $m\subseteq m$ by definition of sub-multiset inclusion. If an exact match is 
not found in $\mathcal{M},$ the function uses multiset-trie to find the closest 
(the largest) sub-multiset of $m$ in $\mathcal{M}$ by decreasing multiplicity of 
elements in $m.$ The parameter $dev$ is used to limit a maximal deviation of 
multiplicity for a particular element in $x$ with respect to $m.$ 
At every level the function tries to proceed with the largest possible multiplicity of 
an element that is provided by $m.$ However, when the function reaches some level 
where it meets a \emph{Null} node and can not go further using path provided by 
$m,$ it decreases the multiplicity of an element 
that corresponds to a current level with respect to the specified maximal deviation. 
Thus, the function can decrease multiplicity of an element or eventually skip it in 
order to find the closest $x\subseteq m.$ The function \textsc{submsetExistence} 
is presented in Algorithm~\ref{alg:subexists}.

@@

\subsection{Super-multiset existence} \label{s:superexists}
The function \textsc{supermsetExistence}($\mathcal{M},m,dev$) checks if there 
exists super-multiset $x$ of a given multiset $m$ in $\mathcal{M},$ such that 
condition $| x[i] - m[i] |\leq dev$ is satisfied, where $1\leq i \leq \sigma.$ By analogy 
to the function \textsc{submsetExistence}, the function \textsc{supermsetExistence} 
starts by searching for an exact match $x=m$ in $\mathcal{M}.$ If an exact 
match is not found in $\mathcal{M},$ the function searches for the closest (the 
smallest) super-multiset $x$ of $m$ in $\mathcal{M}$ by increasing multiplicity 
of elements in $m.$ At every level the function tries to proceed with the smallest 
possible multiplicity of an element that is provided by $m.$ However, when function 
reaches some level where it meets a \emph{Null} node and can not go further using 
path provided by $m,$ it increases the multiplicity of an element that corresponds to a 
current level according to the deviation parameter $dev.$ Thus, the function \textsc{supermsetExistence} 
can increase multiplicity of an element up to $n-1,$ where $n$ is the degree of 
a node in $\mathcal{M},$ to find the closest super-multiset $x\supseteq m$ in 
$\mathcal{M}.$ The function \textsc{supermsetExistence} is presented in 
Algorithm~\ref{alg:superxists}.

@@

\subsection{Get all sub-multisets and get all super-multisets} \label{s:getall}
The algorithms for functions \textsc{getAllSubmsets} and 
\textsc{getAllSupermsets} are based entirely on algorithms for 
\textsc{submsetExistence} and \textsc{supermsetExistence} functions that do not 
terminate on the first existing sub/super-multiset, but store the results and 
continue procedure until all existing sub/super-multisets in $\mathcal{M}$ are 
found and stored. The functions \textsc{getAllSubmsets} and \textsc{getAllSupermsets} 
are presented in Algorithm~\ref{alg:getallsub} and Algorithm~\ref{alg:getallsup} respectively.

In order to record a multiset during multiset-trie traversal we use the variable $x$ in the algorithms.
It is an empty array of size $\sigma$ where we store multiplicities of elements at 
each level as we traverse the tree. The variable $result$ is used as a container for storing 
sub-multisets of $m$ found during traversal. Both variables $x$ and $result$ are presented 
as global, however they could be passed to the recursive function as parameters.

>>>>

%
Let $\mathcal{M}$ be a multiset-trie and let $M$ be a set of multisets that are 
inserted into the multiset-trie $\mathcal{M}.$ We define a type \emph{Multiset} in 
order to use it as a representation of a multiset. The type \emph{Multiset} is 
an array $m$ of constant length $\sigma,$ where $i$-th cell represents the element 
$\phi^{-1}(i)$ from $\Sigma$ with multiplicity $m[i].$ From now on, we 
agree that the first cell of an array has index 1. Let us have an example of a 
\emph{Multiset} instance with $\sigma = 2:$
%
\begin{center}
\begin{tabular}{ccc}
Multiset & & Instance of type Multiset \\
$\{ 1,1,2 \}$ & $\cong $ & 
\begin{tabular}{|c|c|}
\hline 
2 & 1 \\
\hline 
\multicolumn{1}{c}{\tiny 1} & \multicolumn{1}{c}{\tiny 2} \\
\end{tabular}
\end{tabular}
\end{center}
%
The operations supported by the multiset-trie data structure are as follows.
%
\begin{enumerate}
\item \textsc{insert}($\mathcal{M}$, $m$): inserts a multiset $m$ into 
$\mathcal{M}$ if $m\not\in M;$
%
\item \textsc{search}($\mathcal{M}$, $m$): returns true if a multiset $m\in M$ 
for a given $\mathcal{M},$ and returns false otherwise;
%
\item \textsc{delete}($\mathcal{M}$, $m$): returns true if a multiset $m$ was 
successfully deleted from $\mathcal{M},$ and returns false otherwise (in case 
$m\not\in M$);
%
\item \textsc{submsetExistence}($\mathcal{M}$, $m$, $dev$): returns true if 
there exists a $x\in M$ for a given $\mathcal{M}$ such that $x\subseteq m$ 
and $| x[i] - m[i] |\leq dev$ for $1\leq i\leq \sigma$, and returns false otherwise; 
%
\item \textsc{supermsetExistence}($\mathcal{M}$, $m$, $dev$): returns true if 
there exists a $x\in M$ for a given $\mathcal{M}$ such that $x\supseteq m$ 
and $| x[i] - m[i] |\leq dev$ for $1\leq i\leq \sigma$, and returns false otherwise; 
%
\item \textsc{getAllSubmsets}($\mathcal{M}$, $m$, $dev$): returns the set of multisets 
$\{ x \in M : x\subseteq m \wedge |x[i]-m[i]|\leq dev \}$ for a given 
$\mathcal{M},$ where $1\leq i\leq \sigma;$
%
\item \textsc{getAllSupermsets}($\mathcal{M}$, $m$, $dev$): returns the set of multisets 
$\{ x\in M : x\supseteq m \wedge |x[i]-m[i]|\leq dev \}$ for a given $\mathcal{M},$
where $1\leq i\leq \sigma.$
%
\end{enumerate}

In the following subsections, we will present each operation of the multiset-trie 
data structure separately.

@@

\subsection{Insert} \label{s:insert}
The procedure \textsc{insert}($\mathcal{M}$, $m$) inserts a new instance $m$ of 
type Multiset into multiset-trie $\mathcal{M}$. If the complete path already 
exists, then the procedure leaves the structure unchanged. Otherwise, it extends 
partially existing or creates a new complete path. The procedure does not return 
any result. The pseudocode for procedure \textsc{insert} is presented in 
Algorithm~\ref{alg:insert}.

@@

\subsection{Delete} \label{s:delete}
Function \textsc{delete}($\mathcal{M},$ $m$) searches for the complete path 
that corresponds to $m$ in order to remove it. If the path can not be found, the 
function immediately returns false. During the search, the function keeps track of the 
number of children for every node. It marks the nodes that have more than one child 
as \emph{parent nodes} and remembers the label of the child, which is a potential node 
where the sub-tree will be cut to remove the multiset. The parent node is needed to 
perform a removal because the multiset-trie is an explicit data structure. When the search 
is completed, the function removes the sub-tree of the last found parent node and 
returns true. In such a way, after deletion, all the prefixes for other multisets are 
preserved in $\mathcal{M}$ and $m$ is removed. The function \textsc{delete} is 
presented in Algorithm~\ref{alg:delete}.

@@

\subsection{Sub-multiset existence} \label{s:subexists}
The function \textsc{submsetExistence}($\mathcal{M},m,dev$) checks if there exists 
a multiset $x$ in $\mathcal{M},$ that satisfies the condition $x\subseteq m$ and 
$| x[i] - m[i] | \leq dev,$ where $1\leq i \leq \sigma.$ 
The function starts with searching for an exact match $x=m$ in $\mathcal{M},$ 
since $m\subseteq m$ by definition of sub-multiset inclusion. If an exact match is 
not found in $\mathcal{M},$ the function uses multiset-trie to find the closest 
(the largest) sub-multiset of $m$ in $\mathcal{M}$ by decreasing the multiplicity of 
elements in $m.$ The parameter $dev$ is used to limit a maximal deviation of 
multiplicity for a particular element in $x$ with respect to $m.$ 
At every level, the function tries to proceed with the largest possible multiplicity of 
an element that is provided by $m.$ However, when the function reaches some level 
where it meets a \emph{Null} node and can not go further using the path provided by 
$m,$ it decreases the multiplicity of an element 
that corresponds to a current level with respect to the specified maximal deviation. 
Thus, the function can decrease the multiplicity of an element or eventually skip it in 
order to find the closest $x\subseteq m.$ The function \textsc{submsetExistence} 
is presented in Algorithm~\ref{alg:subexists}.

@@

\subsection{Super-multiset existence} \label{s:superexists}
The function \textsc{supermsetExistence}($\mathcal{M},m,dev$) checks if there 
exists super-multiset $x$ of a given multiset $m$ in $\mathcal{M},$ such that 
condition $| x[i] - m[i] |\leq dev$ is satisfied, where $1\leq i \leq \sigma.$ By analogy 
to the function \textsc{submsetExistence}, the function \textsc{supermsetExistence} 
starts by searching for an exact match $x=m$ in $\mathcal{M}.$ If an exact 
match is not found in $\mathcal{M},$ the function searches for the closest (the 
smallest) super-multiset $x$ of $m$ in $\mathcal{M}$ by increasing multiplicity 
of elements in $m.$ At every level, the function tries to proceed with the smallest 
possible multiplicity of an element that is provided by $m.$ However, when the function 
reaches some level where it meets a \emph{Null} node and can not go further using 
the path provided by $m,$ it increases the multiplicity of an element that corresponds to a 
current level according to the deviation parameter $dev.$ Thus, the function \textsc{supermsetExistence} 
can increase multiplicity of an element up to $n-1,$ where $n$ is the degree of 
a node in $\mathcal{M},$ to find the closest super-multiset $x\supseteq m$ in 
$\mathcal{M}.$ The function \textsc{supermsetExistence} is presented in 
Algorithm~\ref{alg:superxists}.

@@

\subsection{Get all sub-multisets and get all super-multisets} \label{s:getall}
The algorithms for functions \textsc{getAllSubmsets} and 
\textsc{getAllSupermsets} are based entirely on algorithms for 
\textsc{submsetExistence} and \textsc{supermsetExistence} functions that do not 
terminate on the first existing sub/super-multiset, but store the results and 
continue the procedure until all existing sub/super-multisets in $\mathcal{M}$ are 
found and stored. The functions \textsc{getAllSubmsets} and \textsc{getAllSupermsets} 
are presented in Algorithm~\ref{alg:getallsub} and Algorithm~\ref{alg:getallsup} respectively.

In order to record a multiset during multiset-trie traversal, we use the variable $x$ in the algorithms.
It is an empty array of size $\sigma$ where we store multiplicities of elements at 
each level as we traverse the tree. The variable $result$ is used as a container for storing 
sub-multisets of $m$ found during traversal. Both variables $x$ and $result$ are presented 
as global, however, they could be passed to the recursive function as parameters.
